Pottery decor as networks on the Middle Niger

### 2024-03-11 analysis/paper/paper.Rmd
small typo changes

decor_20 <- decor_20 
  #isolated nodes are removed
  activate(nodes) |>
  filter(!node_is_isolated())

@@

# Graph of mean edge weight of the different communities
g1 <- ggplot(mean_edge_weight) +
  geom_boxplot(aes(x = community, y = weight, fill = community)) +
  scale_fill_grey(start = 0.5, end  = 1) +
  theme_bw() +
  theme(legend.position = "none") +
  labs(y = "degree centrality",
       x = "community")

>>>>

decor_20 <- decor_20 |> 
  #isolated nodes are removed
  activate(nodes) |>
  filter(!node_is_isolated())

@@

# Graph of mean edge weight of the different communities
g1 <- ggplot(mean_edge_weight) +
  geom_boxplot(aes(x = community, y = weight, fill = community)) +
  scale_fill_grey(start = 0.5, end  = 1) +
  theme_bw() +
  theme(legend.position = "none") +
  labs(y = "mean edge weight",
       x = "community")
